Truthfulness Verification System

### 2011-03-29 proposal/paper.tex
Wikipeida has a kickass api supporting JSON, YAML, XML etc .... Fixed

For disambiguation among the alternative statements, Wikipedia is generally used
as an authoritative source. However, the contents of Wikipedia is not available
in the form that is consumable in a programmatic format. To address such
difficulties a number of projects Yago, DBpedia, Freebase have organized the
massive amount of data in a searchable fashion e.g DBpedia uses SPARQL endpoint,
Freebase uses MQL api. Open source implementation of Python wrappers exist for
both the interfaces exist and appear to be mature enough for our needs.

>>>>

For disambiguation among the alternative statements, Wikipedia is generally used
as an authoritative source. On the other hand DBpedia, Freebase have organized the
massive amount of data in a searchable fashion e.g DBpedia uses SPARQL endpoint,
Freebase uses MQL api. Open source implementation of Python wrappers exist for
both the interfaces exist and appear to be mature enough for our needs.
